Out-of-Sample Comparisons of Overfit Models

### 2014-09-22 paper.tex
Minor tweaks to paper

\title{Out-of-Sample Comparisons of Overfit Models}
\author{Gray Calhoun\thanks{email: gcalhoun@iastate.edu. I
    would like to thank Julian Betts, Helle Bunzel, Marjorie Flavin,
    Nir Jaimovich, Lutz Kilian, Ivana Komunjer, Michael McCracken,
    Seth Pruitt, Ross Starr, Jim Stock, Yixiao Sun, Allan Timmermann,
    Hal White, several anonymous referees, participants at the 2010
    Midwest Economics Association Annual Meetings, the 2010
    International Symposium on Forecasting, the 2010 Joint Statistical
    Meetings, the 2011 NBER-NSF Time-Series
    Conference, and in many seminars at UCSD, and espeically
    Graham Elliott for their valuable suggestions, feedback and advice
    in writing this paper.  I would also like to thank Amit Goyal for
    providing computer code and data for his 2008 RFS paper
    with Ivo Welch \citep{GoW:08}.} \\ Iowa State University}

@@

We focus on linear regression models estimated with a fixed window
for simplicity, but our basic conclusions should be true for other
models and estimation strategies as well.  Under this
asymptotic theory, where the number of regressors $K$ increases with $T$
so that $\lim K/T$ is positive and less than one,
the OLS coefficient estimator is no longer
consistent or asymptotically normal \citep{Hub:73} and has positive
variance in the limit.  We show that, even so, the usual OOS average
is asymptotically normal and can consistently estimate the difference
between the models' generalization error, the expected loss in the
future conditional on the on the data available in period
$T$.%
\footnote{See, for example, \citet{HTF:08} for a discussion of
  generalization error.} %
Under these asymptotics, the generalization
error does not converge to the expected performance of the pseudotrue
models, so existing in-sample and OOS comparisons measure different
quantities and should be expected to give different results for
reasons beyond simple size and power comparisons.  Under our limit theory,
the model that is closer to the true DGP in population can forecast
worse.  In such a situation, a standard in-sample comparison would
correctly reject the null hypothesis that the benchmark is true, and
an OOS comparison would correctly fail to reject the null that the
benchmark is more accurate.%
\footnote{In a pair of papers similar to
  ours, \citet{ClM:12,ClM:12b} study in-sample and OOS tests that
  the larger model has nonzero coefficients that are too close to zero
  to expect the model to forecast more accurately.  Like this paper,
  they argue that the larger model can be true but less accurate.
  However, they focus on an aspect of the DGP that makes this
  phenomenon likely, while we focus on the coefficient estimates that
  produce less accurate forecasts.  Moreover, the implications of our
  asymptotic theories are different and their papers do not provide
  reasons to do OOS comparisons.} %
Also note that, in this situation, a model that performs well
in-sample can perform badly out-of-sample even if there are no
structural breaks or other forms of instability.  Researchers
have argued that a breakdown of in-sample forecasting ability
indicates a structural break (see \citealp{BoH:99}, and
\citealp{StW:03}, among others), but we show that this breakdown
can be caused by overfit as well.

It is important to realize that we are not \emph{advocating} linear
regression for highly overparametrized models. If $K$ is very large
relative to $T$, researchers will often want to use some form of
shrinkage forecast, for example the LASSO \citep{Tib:96} or a factor
model \citep{StW:02,BaN:02}. Our main focus in practice is settings
where $K$ is \emph{moderately} large and it is not clear whether
overfit will dominate the results. In such settings that, it is
important to understand the behavior of different evaluation criteria
when $K$ is large, in case overfit is a concern, and to have reliable
methods for estimating the models' performance, which is the goal of
this paper.

@@

But we also identify new practical limitations for applying the DMW
test to overfit models.
Since the models' coefficients are imprecisely estimated in the limit,
the test sample must be small enough that the model estimated over the
training sample is similar to the one that will be estimated over the
full sample.  In particular, $P/T \to 0$ is required for consistent
estimation of the difference in the two models' performance,
and $P^2/T \to 0$ is required for valid confidence
intervals and inference.  For larger $P$, the OOS comparisons remain
asymptotically normal, but are centered on the forecasting performance
associated with the period-$R$ estimates.  In practice, researchers
typically use large values of $P$, so these studies may be too
pessimistic about their models' future accuracy if they use the DMW
test.  Section~\ref{sec:oostheory} lays out the asymptotic behavior of
the DMW test under this limit theory.

Popular in-sample tests and model selection criteria, like the Wald
test and the AIC, do not help forecasters in this setting. We show
that these statistics do not select the more accurate model when
choosing between overfit models. For many DGPs the Wald test and the
will choose the larger alternative model over a small benchmark model
with probability much greater than its nominal size, regardless of
which model is more accurate, and the AIC behaves similarly. The BIC,
however, chooses the benchmark model with probability approaching one
even when the \emph{alternative} model is more accurate.%
\footnote{Our result holds for a broad class of full-sample
  statistics, but there may be other potential statistics that mimic
  the OOS test and remain valid. Exploring such statistics is left for
  future research.} %
This result holds even though modifications of the $F$-test are valid
under this asymptotic theory, as shown by \citet{BoB:95},
\citet{AkA:00}, \citet{AkP:04}, \citet{Cal:11c}, and \citet{Ana:12},
among others.%
\footnote{Also see \citet{Efr:86,Efr:04} for a discussion of naive
  in-sample loss comparisons.} %
Moreover, under this asymptotic theory, many recent OOS test
statistics, such as those derived by \cite{ClM:01,ClM:05},
\citet{Mcc:07}, and \citet{ClW:06,ClW:07} should have the same
problems as in-sample tests.%
\footnote{Our theoretical results apply directly to \citepos{Mcc:07}
  OOS $t$-test, since it simply proposes more liberal critical values
  for the same test statistic that we study.  Since
  \citet{ClW:06,ClW:07} use a finite length estimation window, our
  asymptotics are incompatible with theirs and prevent us from
  studying their test directly, as well as \citepos{GiW:06} and other
  tests based on \citepos{GiW:06} asymptotics.  But \clws\ test can be
  viewed as a stochastic adjustment to the critical values of the
  usual \oost\ test, so our conclusions should apply informally as
  well.  Specifically, we show that the DMW test rejects with
  probability equal to nominal size when the estimated benchmark model
  is expected to be more accurate, so more liberal critical values
  result in overrejection.} %
These tests are also designed to reject the benchmark when the
alternative model is true, and so they may reject too often when the
benchmark is misspecified but more accurate.  Obviously, since the
distribution of these statistics converges to the normal when $P/T \to
0$ (with the number of regressors fixed), these statistics behave like
the DMW test when $P$ is small, but should overreject the benchmark
when $P$ is large. Section~\ref{sec:insample} presents our theoretical
results for full-sample statistics and Section~\ref{sec:mc} presents
Monte Carlo evidence to support these claims.

Finally, this paper introduces a new method of proof for OOS
statistics.  We use a coupling argument (Berbee's Lemma, 1979) to show
that sequences of OOS loss behave like mixingales when the
underlying series are absolutely regular, even if the forecasts depend
on non-convergent estimators.  Moreover, transformations of these
processes also behave like mixingales when recentered, so 
many arguments used to prove asymptotic
results for Near Epoch Dependent (NED) functions of mixing processes
can be used for these OOS processes with only slight modification.

The rest of the paper proceeds as follows.
Section~\ref{sec:assumptions} introduces our notation and assumptions.
Section~\ref{sec:theory} gives the main theoretical results for the
DMW OOS test, shows that standard in-sample tests reject the
benchmark model too often when it is misspecified but more accurate than the
alternative, and shows that standard model selection methods can run
into similar problems. Section~\ref{sec:mc}
presents a Monte Carlo study supporting our theoretical results.
Section~\ref{sec:empirics} applies the OOS statistic to
\citepos{GoW:08} dataset for equity premium prediction, and
Section~\ref{sec:conclusion} concludes.  Proofs and supporting results
are listed in the Appendix.

@@

Statistics like $\oost$ have a long history in empirical economics
because they capture an intuitive idea of model fit: that a good model
should be able to forecast well on new data. \cite{MeR:83}
use such a statistic to study exchange rate models and find that none
of the models that existed at the time of their study outperform a
random walk. This finding has been remarkably durable and has spawned
an enormous literature; see \cite{Mar:95}, \cite{KiT:03},
\cite{CCP:05}, \cite{EnW:05}, \cite{Ros:05}, and \cite{BWB:10}, among
many others.

@@

In the first result, we show that
$\sqrt{P} (\oosA - \E_R \oosA)$ is asymptotically normal as $P \to
\infty$. This application of the CLT is complicated by a hidden source
of dependence---the training sample estimators $\bh{iR}$. Under
conventional asymptotic theory, we would replace each $\bh{iR}$ with
its pseudotrue value $\theta_i$ and apply the CLT to $\sqrt{P}
L(y_{t+\h} - x_{it}'\theta_i)$, with some complications potentially
arising from the replacement (as in \citealp{Wes:96},
\citealp{ClM:01}, or \citealp{Mcc:07}, for example). But we can not
make that replacement here, because our asymptotic approximation
prevents $x_{it}'\bh{iR}$ from converging to $x_{it}'\theta_i$.

@@

The next Lemma connects $E_R \oosA$ to $\E_T \oosB$, the difference in
the models' generalization error. Under conventional asymptotics,
these quantities are generally close. But they are not for overfit
models, and the models will tend to forecast better when estimated over the
full sample than over the training sample. Consequently, OOS
comparisons will penalize overfit models too much unless the test
sample is small relative to the total data set.

@@

Finally, we can use Lemmas~\ref{res-mixingale}
and~\ref{res-convergence} to show that the DMW test is asymptotically
normal and centered at $\E_T \oosB$, as long as
Assumption~\ref{asmp-4}b holds. This theorem only establishes the
asymptotic distribution, though.

@@

When $K_1$ and $K_2$ are fixed, West's (1996) and McCracken's (2007)
asymptotic theories apply and the \oost\ test remains normal as long
as $P/T \to 0$, even if $\sigma^2 \to 0$. Under that asymptotic
approximation, the variance will converge to zero whenever the true
DGP is nested in both of the forecasting models. The same principles
may apply in our setting if $K_1$ and $K_2$ grow slowly, so $K_2/T \to
0$. It is likely that a second order expansion along the lines of
\citet{Mcc:07} would lead to asymptotic normality for that
intermediate case, but we leave that issue to future research.

@@

\begin{thm}\label{res:oostest}
  Suppose that the conditions of Theorem
  \ref{res-oost} hold. Then each of the usual Gaussian
  confidence intervals,
  \begin{gather}
    [\oosA - z_{\alpha/2} \, \sh /
    \sqrt{P}, \oosA + z_{\alpha/2} \sh / \sqrt{P}],\label{interval-twosided} \\
    [\oosA - z_{\alpha} \, \sh / \sqrt{P}, +\infty), \label{interval-greater}
    \intertext{and}
    (-\infty, \oosA + z_{\alpha} \, \sh / \sqrt{P}],
  \end{gather}
  contains $\E_T\oosB$ with probability $\alpha$ in the limit, with
  $z_{\alpha}$ the $1-\alpha$ quantile of the standard normal
  distribution. If, in addition, $\lim \Pr[\E_T \oosB \leq 0]$ is
  positive then
  \begin{equation}\label{eq:23}
    \lim \Pr[P^{1/2}\oosA/\sh > z_{\alpha} \mid \E_T
    \oosB \leq 0] \leq \alpha.
  \end{equation}
\end{thm}
\noindent
The results for confidence intervals in Theorem~\ref{res:oostest}
follow immediately from Theorem~\ref{res-oost},
but~\eqref{eq:23} requires additional steps.

@@

In this subsection we look at the behavior of some full-sample
statistics under the same asymptotic theory as before.  We show that
these statistics, which include common tests such as the Wald test as
well as model selection criteria such as the AIC, do not measure the
models' generalization error and consequently do not indicate which
model will be more accurate in the future. Some of these statistics
will tend to choose the larger model regardless of which model will be
more accurate in the future, whereas others tend to choose the smaller
model.  This is a different issue than whether or not full-sample
tests are valid for testing hypotheses about the pseudotrue
coefficients of the models; as \citet{Cal:11c} and \citet{Ana:12}
demonstrate, variations of the Wald test can be valid for those
hypotheses under increasing-$K$ asymptotics.%
\footnote{\citet{Ana:12} shows that the Wald test is invalid in
  general and gives an adjustment that corrects the critical values;
  he also shows that the $F$-test is asymptotically valid under
  certain conditions on the distribution of the regressors.
  \citet{Cal:11c} shows that the $F$-test is asymptotically invalid
  without Anatolyev's constraint, even under homoskedasticity, and
  provides a correction that gives valid tests.  Both papers only
  consider independent observations.} %
To simplify the presentation and the intuition we only derive results
for nested models and for MSE loss, but the conclusions hold much more
generally.%
\footnote{Also, define $M_1 = [I_{K_1} \ 0_{K_1 \times (K_2 - K_1)}]$
  and $M_2 = [0_{(K_2 - K_1) \times K_2} \ I_{K_2 - K_1}]$ as the
  selection matrices that return the first $K_1$ and the last $K_2 -
  K_1$ elements of $\theta_2$, and assume that the regressors are
  ordered so that the first $K_1$ elements of $x_{2,t}$ correspond to
  $x_{1,t}$.} %

@@

  Then there exist DGPs satisfying these assumptions such that
  \begin{equation}\label{eq:11}
    \liminf_{T \to \infty} \E( \Lambda \mid \E_T \oosB \leq 0 )
    \to^p \gamma > 1/2 - \delta.
  \end{equation}
\end{thm}

As we state above,~\eqref{eq:11} means that, with high probability,
the benchmark model is rejected even when it is more accurate. In
general, $\delta$ can be made arbitrarily small by increasing the
region enclosed by $\1\{\bh{2T}'M_2' V_T M_2\bh{2T}\}$ and DGPs can be
chosen to put $\gamma$ arbitrarily close to 1 while still satisfying
the assumptions of the Theorem.  The DGPs and
statistics used in Theorem~\ref{res:insample1} are simple and
common. They include correctly specified linear models with normal and
homoskedastic errors; and the statistics that meet the restrictions on
$\Lambda$ include the $F$-test and AIC.

For example, the $F$-statistic to test the null hypothesis that the
benchmark model is correctly specified is known to have the form
\begin{equation*}
  F = \frac{\bh{2T}' M_2' ( M_2 (X_{2T}'X_{2T})^{-1} M_2' )^{-1} M_2
    \bh{2T}}{s^2 (K_2 - K_1)}
\end{equation*}
where $s^2$ is the usual estimator of the variance of the regression
error. Then let $c$ be any number greater than 1 and define
\begin{equation*}
  V_T = M_2' \big( M_2 \big(\tfrac{1}{s^2 (K_2 - K_1)} X_{2T}'X_{2T}\big)^{-1}
  M_2' \big)^{-1} M_2'.
\end{equation*}
If Assumption~\ref{asmp-2} holds and $s^2$ is consistent then $V_T$
has uniformly bounded eigenvalues and has rank $K_2 - K_1$, so it
satisfies~\eqref{eq:25}.%
\footnote{If it is surprising that these conditions hold for any $c >
  1$, remember that the $F$ random variable converges to 1 in
  probability as both degrees of freedom diverge to $\infty$ since its
  numerator and denominator both obey the LLN.} %
Robust variations of the Wald test can obviously satisfy~\eqref{eq:25}
for similar reasons, and the AIC for nested linear models is
equivalent to using the $F$-test with the critical value %
$(e^{2 (K_2 - K_1) / T} - 1) \cdot (T - K_2) / (K_2 - K_1)$, %
which converges to a finite limit, so the AIC satisfies~\eqref{eq:25}
as well.

@@

This behavior is formalized in Theorem~\ref{res:insample2}.
\begin{thm}\label{res:insample2}
  Suppose Assumptions~\ref{asmp-1}--\ref{asmp-4} hold, let $L(e) =
  e^2$, and let $\Lambda$ be a model selection statistic as in
  Theorem~\ref{res:insample1}. Also assume that, for any finite scalar
  $c$,
  \begin{equation}\label{eq:27}
    \Pr[\Lambda \leq \1\{\bh{2T}'M_2' M_2\bh{2T} > c \}] \to 1
    \quad \text{as } T \to \infty.
  \end{equation}

@@

The condition~\ref{eq:27} requires that the acceptance region of
$\Lambda$ eventually contains any finite cylinder centered at the
origin. Again,~\eqref{eq:15} implies that statistics like the BIC
will always choose the smaller model for some DGPs, even when the
larger model will give more accurate forecasts. Both models may be
overfit, in that both $K_1/T$ and $K_2/T$ may both be positive in the
limit; the key is that $(K_2 - K_1)/T$ is also positive in the limit.

@@

This subsection illustrates the previous theoretical results with a
concrete Let $L(e) = e^2$ and $h = 1$. Suppose that the benchmark is
nested in the alternative and $(x_{2t}, \e_{2,t+1}) \sim i.i.d.\
N(0,I)$, and let $y_{t+1} = x_{2t}'\theta_2 + \e_{2,t+1}$
be the DGP. Also assume that $K_2/T \to c_2$ and $K_1 / T \to c_1 <
c_2$.

The first part of this subsection shows how the assumptions in
Section~\ref{sec:asmp} are satisfied and the second part
demonstrates asymptotic normality of the DMW OOS $t$-test. The third
part explicitly shows that $\E_R \oosA$ converges to $\E_T \oosB$ only
when the test sample is small. And the last part demonstrates that the
$F$-test, AIC, and BIC do not indicate which model will be more
accurate in the future, even in this simple example.

@@

We will go through the assumptions one by one. The first Assumption is
a condition on the dependence and moments of the process. Since the
DGP is i.i.d. Normal, these conditions are satisfied trivially.

@@

Finally, Assumption~\ref{asmp-4} deals with the choice of test and
training sample and holds automatically. And Assumption~\ref{asmp-5}
requires the kernel of the HAC variance estimator to be continuous at
zero; it is straightforward to construct an estimator that satisfies
this condition. However, in this section we will use the estimator
\begin{equation*}
  \sh^2 = \frac{1}{n} \sum_{t=R+1}^{T-1} (D_t - \oosA)^2
\end{equation*}
which does not satisfy Assumption~\ref{asmp-5} but nevertheless is
consistent for the conditional variance of $\oosA$ because the
underlying observations are independent.

@@

\bibliographystyle{abbrvnat}
\bibliography{references}
\clearpage

>>>>

\title{Out-of-Sample Comparisons of Overfit Models}
\author{Gray Calhoun\thanks{email: gcalhoun@iastate.edu. I
    would like to thank Julian Betts, Helle Bunzel,
    St\'ephane Bonhomme, Marjorie Flavin,
    Nir Jaimovich, Lutz Kilian, Ivana Komunjer, Michael McCracken,
    Seth Pruitt, Ross Starr, Jim Stock, Yixiao Sun, Allan Timmermann,
    Hal White, several anonymous referees, participants at the 2010
    Midwest Economics Association Annual Meetings, the 2010
    International Symposium on Forecasting, the 2010 Joint Statistical
    Meetings, the 2011 NBER-NSF Time-Series
    Conference, and in many seminars at UCSD, and especially
    Graham Elliott for their valuable suggestions, feedback and advice
    in writing this paper.  I would also like to thank Amit Goyal for
    providing computer code and data for his 2008 RFS paper
    with Ivo Welch \citep{GoW:08}.} \\ Iowa State University}

@@

We focus on linear regression models estimated with a fixed window
for simplicity, but our basic conclusions should be true for other
models and estimation strategies as well.  Under this
asymptotic theory, where the number of regressors $K$ increases with $T$
so that the limit of $K/T$ is positive and less than one,
the OLS coefficient estimator is no longer
consistent or asymptotically normal \citep{Hub:73} and has positive
variance in the limit.  We show that, even so, the usual OOS average
is asymptotically normal and can consistently estimate the difference
between the models' generalization error, the expected loss in the
future conditional on the on the data available in period
$T$.%
\footnote{See, for example, \citet{HTF:08} for a discussion of
  generalization error.} %
Under these asymptotics, the generalization
error does not converge to the expected performance of the pseudotrue
models, so existing in-sample and OOS comparisons measure different
quantities and should be expected to give different results for
reasons beyond simple size and power comparisons.  Under our limit theory,
the model that is closer to the true DGP in population can forecast
worse.  In such a situation, a standard in-sample comparison would
correctly reject the null hypothesis that the benchmark is true, and
an OOS comparison would correctly fail to reject the null that the
benchmark is more accurate.%
\footnote{In a pair of papers similar to
  ours, \citet{ClM:12,ClM:12b} study in-sample and OOS tests that
  the larger model has nonzero coefficients that are too close to zero
  to expect the model to forecast more accurately.  Like this paper,
  they argue that the larger model can be true but less accurate.
  However, they focus on an aspect of the DGP that makes this
  phenomenon likely, while we focus on the coefficient estimates that
  produce less accurate forecasts.  Moreover, the implications of our
  asymptotic theories are different and their papers do not provide
  reasons to do OOS comparisons.} %
Also note that, in this situation, a model that performs well
in-sample can perform badly out-of-sample even if there are no
structural breaks or other forms of instability.  Researchers
have argued that a breakdown of in-sample forecasting ability
indicates a structural break (see \citealp{BoH:99}, and
\citealp{StW:03}, among others), but we show that this breakdown
can be caused by overfit as well.

It is important to realize that we are not \emph{advocating} linear
regression for highly overparametrized models. If $K$ is very large
relative to $T$, researchers will often want to use some form of
shrinkage forecast, for example the LASSO \citep{Tib:96} or a factor
model \citep{StW:02,BaN:02}. Our main focus is practical settings
where $K$ is \emph{moderately} large and it is not clear whether
overfit will dominate the results. In these settings it is
crucial to understand the behavior of different evaluation criteria
when $K$ is large, in case overfit does turn out to be a concern, and to have reliable
methods for estimating these overfit models' performance. This is the goal of
this paper.

@@

But we also identify new practical limitations for applying the DMW
test to overfit models.
Since the models' coefficients are imprecisely estimated in the limit,
the test sample must be small enough that the model estimated over the
training sample is similar to the one that will be estimated over the
full sample.  In particular, $P/T \to 0$ is required for consistent
estimation of the difference in the two models' performance,
and $P^2/T \to 0$ is required for valid confidence
intervals and inference.  For larger $P$, the OOS comparisons remain
asymptotically normal, but are centered on the forecasting performance
associated with the period $R$ estimates.  In practice, researchers
typically use large values of $P$, so these studies may be too
pessimistic about their models' future accuracy if they use the DMW
test.  Section~\ref{sec:oostheory} lays out the asymptotic behavior of
the DMW test under this limit theory.

Popular in-sample tests and model selection criteria, like the Wald
test and the AIC, do not help forecasters in this setting. We show
that these statistics do not select the more accurate model when
choosing between overfit models. For many DGPs the Wald test
will choose the larger model over a small benchmark
with probability much greater than its nominal size, regardless of
which model is more accurate, and the AIC behaves similarly. The BIC,
however, chooses the benchmark model with probability approaching one
even when the \emph{alternative} model is more accurate.%
\footnote{Our result holds for a broad class of full-sample
  statistics, but there may be other potential statistics that mimic
  the OOS test and remain valid. Exploring such statistics is left for
  future research.} %
This result holds even though modifications of the $F$-test are valid
under this asymptotic theory, as shown by \citet{BoB:95},
\citet{AkA:00}, \citet{AkP:04}, \citet{Cal:11c}, and \citet{Ana:12},
among others.%
\footnote{Also see \citet{Efr:86,Efr:04} for a discussion of naive
  in-sample loss comparisons.} %
Moreover, under this asymptotic theory, many recent OOS test
statistics, such as those derived by \cite{ClM:01,ClM:05},
\citet{Mcc:07}, and \citet{ClW:06,ClW:07} should have the same
problems as in-sample tests.%
\footnote{Our theoretical results apply directly to \citepos{Mcc:07}
  OOS $t$-test, since it simply proposes more liberal critical values
  for the same test statistic that we study.  Since
  \citet{ClW:06,ClW:07} use a finite length estimation window, our
  asymptotics are incompatible with theirs and prevent us from
  studying their test directly, as well as \citepos{GiW:06} and other
  tests based on \citepos{GiW:06} asymptotics.  But \clws\ test can be
  viewed as a stochastic adjustment to the critical values of the
  usual \oost\ test, so our conclusions should apply informally as
  well.  Specifically, we show that the DMW test rejects with
  probability equal to nominal size when the estimated benchmark model
  is expected to be more accurate, so more liberal critical values
  result in overrejection.} %
These tests are also designed to reject the benchmark when the
alternative model is true, and so they may reject too often when the
benchmark is misspecified but more accurate.  Obviously, since the
distribution of these statistics converges to the normal when $P/T \to
0$ (with the number of regressors fixed), these statistics behave like
the DMW test when $P$ is small, but should overreject the benchmark
when $P$ is large. Section~\ref{sec:insample} presents our theoretical
results for full-sample statistics and Section~\ref{sec:mc} presents
Monte Carlo evidence to support these claims.

Finally, this paper introduces a new method of proof for OOS
statistics.  We use a coupling argument (Berbee's Lemma, 1979) to show
that sequences of OOS loss behave like mixingales when the
underlying series are absolutely regular, even if the forecasts depend
on non-convergent estimators.  Moreover, we also show that transformations of these
processes behave like mixingales after they are appropriately recentered, so
many arguments used to prove asymptotic
results for Near Epoch Dependent (NED) functions of mixing processes
can be used for these OOS processes with only slight modification.

The rest of the paper proceeds as follows.
Section~\ref{sec:assumptions} introduces our notation and assumptions.
Section~\ref{sec:theory} gives the main theoretical results for the
DMW OOS test, shows that standard in-sample tests reject the
benchmark model too often when it is misspecified but more accurate than the
alternative, and shows that standard model selection methods can run
into similar problems. Section~\ref{sec:theory} also presents an
example DGP that illustrates these results. Section~\ref{sec:mc}
presents a Monte Carlo study supporting our theoretical results.
Section~\ref{sec:empirics} applies the OOS statistic to
\citepos{GoW:08} dataset for equity premium prediction, and
Section~\ref{sec:conclusion} concludes.  Proofs and supporting results
are listed in the Appendix.

@@

Statistics like $\oost$ have a long history in empirical economics
because they capture an intuitive idea of model fit: that a good model
should be able to forecast well on new data. \cite{MeR:83}
use such a statistic to study exchange rate models and find that none
of the models that existed at the time of their study outperform a
random walk. This finding has been remarkably durable and has spawned
an enormous literature; see \cite{Mar:95}, \cite{KiT:03},
\cite{CCP:05}, \cite{EnW:05}, \cite{Ros:05}, and \cite{BWB:10}, among
many others. Research in financial markets has found a similar pattern,
e.g. \cite{BoH:99}, \citet{GoW:08,GoW:03}, and \citet{Tim:08}.

@@

In the first result, we show that
$\sqrt{P} (\oosA - \E_R \oosA)$ is asymptotically normal as $P \to
\infty$. This application of the CLT is complicated by a hidden source
of dependence---the training sample estimators $\bh{iR}$. Under
conventional asymptotic theory, we would replace each $\bh{iR}$ with
its pseudotrue value $\theta_i$ and apply the CLT to
$L(y_{t+\h} - x_{it}'\theta_i)$, with some complications potentially
arising from the replacement (as in \citealp{Wes:96},
\citealp{ClM:01}, or \citealp{Mcc:07}, for example). But we can not
make that replacement here, because our asymptotic approximation
prevents $x_{it}'\bh{iR}$ from converging to $x_{it}'\theta_i$.

@@

The next Lemma connects $E_R \oosA$ to $\E_T \oosB$, the difference in
the models' generalization error. Under conventional asymptotics,
these quantities are generally close. But they are not for overfit
models and the models will tend to forecast better when estimated over the
full sample than over the training sample. Consequently, OOS
comparisons will penalize overfit models too much unless the test
sample is small relative to the total data set.

@@

Finally, we can use Lemmas~\ref{res-mixingale}
and~\ref{res-convergence} to show that the DMW test is asymptotically
normal and centered at $\E_T \oosB$, as long as
Assumption~\ref{asmp-4}b holds.

@@

If $K_1$ and $K_2$ were finite, West's (1996) and McCracken's (2007)
asymptotic theories would apply and the \oost\ test would remain normal as long
as $P/T \to 0$, even if $\sigma^2 \to 0$. Under that asymptotic
approximation, the variance will converge to zero whenever the true
DGP is nested in both of the forecasting models. The same principles
may also apply if $K_1$ and $K_2$ grow slowly, with $K_2/T \to
0$. It is likely that a second order expansion along the lines of
\citet{Mcc:07} would lead to asymptotic normality for that
intermediate case, but we leave that issue to future research.

@@

\begin{thm}\label{res:oostest}
  Suppose that the conditions of Theorem
  \ref{res-oost} hold. Then each of the usual Gaussian
  confidence intervals,
  \begin{gather}
    [\oosA - z_{\alpha/2} \, \sh /
    \sqrt{P}, \oosA + z_{\alpha/2} \sh / \sqrt{P}],\label{interval-twosided} \\
    [\oosA - z_{\alpha} \, \sh / \sqrt{P}, +\infty), \label{interval-greater}
    \intertext{and}
    (-\infty, \oosA + z_{\alpha} \, \sh / \sqrt{P}],
  \end{gather}
  contains $\E_T\oosB$ with probability $\alpha$ in the limit, with
  $z_{\alpha}$ the $1-\alpha$ quantile of the standard normal
  distribution. If, in addition, $\lim \Pr[\E_T \oosB \leq 0]$ is
  positive then
  \begin{equation}\label{eq:23}
    \lim \Pr[P^{1/2}\oosA/\sh > z_{\alpha} \mid \E_T
    \oosB \leq 0] \leq \alpha.
  \end{equation}
\end{thm}
\noindent
The results for confidence intervals in Theorem~\ref{res:oostest}
follow immediately from Theorem~\ref{res-oost},
but~\eqref{eq:23} requires additional proof.

@@

In this subsection we look at the behavior of some full-sample
statistics under the same asymptotic theory as before.  We show that
these statistics, which include common tests such as the Wald test as
well as model selection criteria such as the AIC, do not measure the
models' generalization error and consequently do not indicate which
model will be more accurate in the future. Some of these statistics
will tend to choose the larger model regardless of which model will be
more accurate in the future, whereas others tend to choose the smaller
model.  This is a different issue than whether or not full-sample
tests are valid for testing hypotheses about the pseudotrue
coefficients of the models; as \citet{Cal:11c} and \citet{Ana:12}
demonstrate, variations of the Wald test can be valid for those
hypotheses under increasing-$K$ asymptotics.%
\footnote{\citet{Ana:12} shows that the Wald test is invalid in
  general and gives an adjustment that corrects the critical values;
  he also shows that the $F$-test is asymptotically valid under
  certain conditions on the distribution of the regressors.
  \citet{Cal:11c} shows that the $F$-test is asymptotically invalid
  without Anatolyev's constraint, even under homoskedasticity, and
  provides a correction that gives valid tests.  Both papers only
  consider independent observations.} %
To simplify the presentation and the intuition we only derive results
for nested models and for MSE loss, but the conclusions hold much more
generally.%
\footnote{In this section, we define $M_1 = [I_{K_1} \ 0_{K_1 \times (K_2 - K_1)}]$
  and $M_2 = [0_{(K_2 - K_1) \times K_2} \ I_{K_2 - K_1}]$ as the
  selection matrices that return the first $K_1$ and the last $K_2 -
  K_1$ elements of $\theta_2$, and assume that the regressors are
  ordered so that the first $K_1$ elements of $x_{2,t}$ correspond to
  $x_{1,t}$.} %

@@

  Then there exist DGPs satisfying these assumptions such that
  \begin{equation}\label{eq:11}
    \liminf_{T \to \infty} \E( \Lambda \mid \E_T \oosB \leq 0 ) \geq 1/2.
  \end{equation}
\end{thm}

As we state above,~\eqref{eq:11} means that, with high probability,
the benchmark model is rejected even when it is more accurate. In
general, $\delta$ can be made arbitrarily small by increasing the
region enclosed by $\1\{\bh{2T}'M_2' V_T M_2\bh{2T}\}$ and DGPs can be
chosen to put the limiting quantity in~\eqref{eq:11}
arbitrarily close to 1 while still satisfying
the assumptions of the Theorem.  The DGPs and
statistics used in Theorem~\ref{res:insample1} are simple and
common. They include correctly specified linear models with normal and
homoskedastic errors; and the statistics that meet the restrictions on
$\Lambda$ include the $F$-test and AIC.

For example, the $F$-statistic for the null hypothesis that the
benchmark model is correctly specified is known to have the form
\begin{equation*}
  F = \frac{\bh{2T}' M_2' ( M_2 (X_{2T}'X_{2T})^{-1} M_2' )^{-1} M_2
    \bh{2T}}{s^2 (K_2 - K_1)}
\end{equation*}
where $s^2$ is the usual estimator of the variance of the regression
error. Then let $c$ be any number greater than 1 and define
\begin{equation*}
  V_T = M_2' \big( M_2 \big(\tfrac{1}{s^2 (K_2 - K_1)} X_{2T}'X_{2T}\big)^{-1}
  M_2' \big)^{-1} M_2'.
\end{equation*}
If Assumption~\ref{asmp-2} holds and $s^2$ is consistent then $V_T$
has uniformly bounded eigenvalues and has rank $K_2 - K_1$, so it
satisfies~\eqref{eq:25}.
Robust variations of the Wald test can obviously satisfy~\eqref{eq:25}
for similar reasons, and the AIC for nested linear models is
equivalent to using the $F$-test with the critical value %
$(e^{2 (K_2 - K_1) / T} - 1) \cdot (T - K_2) / (K_2 - K_1)$, %
which converges to a finite limit, so the AIC satisfies~\eqref{eq:25}
as well.

@@

This behavior is formalized in Theorem~\ref{res:insample2}.
\begin{thm}\label{res:insample2}
  Suppose Assumptions~\ref{asmp-1}--\ref{asmp-4} hold, let $L(e) =
  e^2$, and let $\Lambda$ be a model selection statistic as in
  Theorem~\ref{res:insample1}. Also assume that, for any finite scalar
  $c$,
  \begin{equation}\label{eq:27}
    \Pr[\Lambda \leq \1\{\bh{2T}'M_2'J M_2\bh{2T} > c \}] \to 1
    \quad \text{as } T \to \infty.
  \end{equation}

@@

The condition~\eqref{eq:27} requires that the acceptance region of
$\Lambda$ eventually contains any finite cylinder centered at the
origin. Again,~\eqref{eq:15} implies that statistics like the BIC
will always choose the smaller model for some DGPs, even when the
larger model will give more accurate forecasts. Both models may be
overfit, in that both $K_1/T$ and $K_2/T$ may both be positive in the
limit; the key is that $(K_2 - K_1)/T$ is also positive in the limit.

@@

This subsection illustrates the previous theoretical results with a
concrete example. Let $L(e) = e^2$ and $h = 1$. Suppose that the benchmark is
nested in the alternative and $(x_{2t}, \e_{2,t+1}) \sim i.i.d.\
N(0,I)$, and let $y_{t+1} = x_{2t}'\theta_2 + \e_{2,t+1}$
be the DGP. Also assume that $K_2/T \to c_2$ and $K_1 / T \to c_1 <
c_2$.

The first part of this subsection shows how the assumptions in
Section~\ref{sec:asmp} are satisfied and the second part
demonstrates asymptotic normality of the DMW \oost\ test. The third
part explicitly shows that $\E_R \oosA$ converges to $\E_T \oosB$ only
when the test sample is small. And the last part demonstrates that the
$F$-test does not indicate which model will be more
accurate in the future, even in this simple example.

@@

We will go through the assumptions one by one. The first is
a condition on the dependence and moments of the process. Since the
DGP is i.i.d. Normal, these conditions are satisfied trivially.

@@

Finally, Assumption~\ref{asmp-4} deals with the choice of test and
training sample and holds automatically. And Assumption~\ref{asmp-5}
requires the kernel of the HAC variance estimator to be continuous at
zero; it is straightforward to construct an estimator that satisfies
this condition. However, in this section we will use the estimator
\begin{equation*}
  \sh^2 = \frac{1}{P} \sum_{t=R+1}^{T-1} (D_t - \oosA)^2
\end{equation*}
which does not satisfy Assumption~\ref{asmp-5} but nevertheless is
consistent for the conditional variance of $\oosA$ because the
underlying observations are independent.

@@

\clearpage
